Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-27 cbm-rbd-paper.tex
survsign first and in separate section, brakesys instead of bridgesys

@@

***RUL/RLD via survival signature,
posterior predictive distributions,
system reliability distribution (RUL/RLD) as output,

@@

We can analyze systems of arbitrary layout, consisting of components of $k=1,\ldots,K$ different types,
where for each type $k$, there are $N_k$ exchangeable components in the system.
As an example, Figure~\ref{fig:bridge-layout} depicts the reliability block diagram of a bridge type system
with three component types $A$, $B$, $C$, where $N_A=4$, $N_B=1$, and $N_C=1$.

@@

\begin{figure}
\centering
\begin{tikzpicture}
[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={very thick, to path={-| (\tikztotarget)}},
 vh path/.style={very thick, to path={|- (\tikztotarget)}}]
%\begin{scope}[scale=0.75]
\node[type1] (T1-2) at ( 1.4, 1) {$A_1$};
\node[type1] (T1-3) at ( 1.4,-1) {$A_2$};
\node[type1] (T1-5) at ( 4.2, 1) {$A_3$};
\node[type1] (T1-6) at ( 4.2,-1) {$A_4$};
\node[type2] (T2)   at ( 2.8, 0) {$B_1$};
\node[type3] (T3)   at ( 5.6, 0) {$C_1$};
\coordinate (start) at (0  ,0);
\coordinate (end)   at (6.3,0);
\coordinate (bista) at (0.7,0);
\coordinate (biend) at (4.9,0);
\path (bista)     edge[hv path] (start)
                  edge[vh path] (T1-2.west)
                  edge[vh path] (T1-3.west)
      (T1-2.east) edge[hv path] (T2.north)
      (T1-3.east) edge[hv path] (T2.south)
      (T2.north)  edge[vh path] (T1-5.west)
      (T2.south)  edge[vh path] (T1-6.west)
      (biend)     edge[vh path] (T1-5.east)
                  edge[vh path] (T1-6.east)
                  edge[hv path] (T3.west)
      (T3.east)   edge[hv path] (end);
%\end{scope}
\end{tikzpicture}
\caption{Reliability block diagram for a `bridge' type system with three component types $A$, $B$, $C$.
Note that this system layout cannot be expressed as a nesting of series and parallel layouts.
The corresponding survival signature $\Phi(l_A,l_B,l_C)$ is given in Table~\ref{tab:bridge-survsign}.}
\label{fig:bridge-layout}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{ccclccccl}
  \toprule
$l_A$ & $l_B$ & $l_C$ & $\Phi$ & \quad & $l_A$ & $l_B$ & $l_C$ & $\Phi$\\ 
  \midrule
0 & 0 & 1 & 0    & & 0 & 1 & 1 & 0 \\ 
1 & 0 & 1 & 0    & & 1 & 1 & 1 & 0 \\ 
2 & 0 & 1 & 0.33 & & 2 & 1 & 1 & 0.67 \\ 
3 & 0 & 1 & 1    & & 3 & 1 & 1 & 1 \\ 
4 & 0 & 1 & 1    & & 4 & 1 & 1 & 1 \\ 
   \bottomrule
\end{tabular}
\caption{Survival signature $\Phi(l_A,l_B,l_C)$ for the bridge system from Figure~\ref{fig:bridge-layout},
omitting all rows with $l_C=0$, since $\Phi(l_A,l_B,0)=0$ for all $l_A$ and $l_B$.}
\label{tab:bridge-survsign}
\end{table}

\subsection{Reliability functions for complex systems using the survival signature}
\label{sec:sysrel}

Here we describe how system reliability functions, given fixed component models,
can be efficiently calculated using the survival signature.
We will show in Section~\ref{sec:sysreltnow}
how this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
giving us the RUL/RLD distribution on which we base our adaptive maintenance policy.

We consider systems of arbitrary reliability block diagram layout,
consisting of components of $K$ different types,
where there are $N_k$ components of type $k$ in the system,
and the total number of components in the system is $\sum_{k=1}^K N_k = N$.
An example system reliability block diagram is given in Figure~\ref{fig:bridge-layout}.
Note that this system cannot be described as a nesting of series and parallel subsystems.
%This system is observed until time $\tnow$,
%leading to censored observation of certain component lifetimes within the system.

As an example, the survival signature for the system in Figure~\ref{fig:bridge-layout} is given in Table~\ref{tab:bridge-survsign}.

>>>>

\section{Reliability functions for complex systems using the survival signature}
\label{sec:sysrel}

Here we describe how the system reliability function, given fixed component models and the system layout,
can be efficiently calculated using the survival signature.
We will show in Section~\ref{sec:sysreltnow}
how this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
giving us the residual life distribution on which we base our adaptive maintenance policy.

We can analyze systems of arbitrary reliability block diagram layout,
consisting of components of $K$ different types,
where there are $N_k$ exchangeable components of type $k$ in the system,
and the total number of components in the system is $\sum_{k=1}^K N_k = N$.

As a running example, we consider a simplified automotive braking system
consisting of four component types $M$, $H$, $C$ and $P$,
with reliability block diagram as depicted in Figure~\ref{fig:brakesys-layout}.
The master brake cylinder ($M$) activates all four wheel brake cylinders ($C_1$ -- $C_4$),
which in turn actuate a braking pad assembly each ($P_1$ -- $P_4$).
The hand brake mechanism ($H$) directly actuates the brake pad assemblies $P_3$ and $P_4$;
the vehicle brakes when at least one brake pad assembly is actuated.
Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
%This system is observed until time $\tnow$,
%leading to censored observation of certain component lifetimes within the system.

\begin{figure}
\centering
\begin{tikzpicture}
[typeM/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
 typeC/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
 typeP/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
 typeH/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
 type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 cross/.style={cross out,draw=red,very thick,minimum width=9mm, minimum height=7mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
\begin{scope}[xscale=1.5, yscale=1.2]
\node[typeM] (M)    at ( 0  , 0  ) {$M$};
\node[typeC] (C1)   at ( 1  , 1.5) {$C_1$};
\node[typeC] (C2)   at ( 1  , 0.5) {$C_2$};
%\node[cross]        at ( 1  , 0.5) {};
\node[typeC] (C3)   at ( 1  ,-0.5) {$C_3$};
%\node[cross]        at ( 1  ,-0.5) {};
\node[typeC] (C4)   at ( 1  ,-1.5) {$C_4$};
\node[typeP] (P1)   at ( 2  , 1.5) {$P_1$};
\node[typeP] (P2)   at ( 2  , 0.5) {$P_2$};
%\node[cross]        at ( 2  , 0.5) {};
\node[typeP] (P3)   at ( 2  ,-0.5) {$P_3$};
%\node[cross]        at ( 2  ,-0.5) {};
\node[typeP] (P4)   at ( 2  ,-1.5) {$P_4$};
\node[typeH] (H)    at ( 0  ,-1  ) {$H$};
\coordinate (start)  at (-0.7, 0);
\coordinate (startC) at ( 0.5, 0);
\coordinate (startH) at (-0.4, 0);
\coordinate (Hhop1)  at ( 0.4,-1);
\coordinate (Hhop2)  at ( 0.6,-1);
\coordinate (endP)   at ( 2.5, 0);
\coordinate (end)    at ( 2.8, 0);
\path (start)     edge[hv path] (M.west)
      (M.east)    edge[hv path] (startC)
      (startC)    edge[vh path] (C1.west)
                  edge[vh path] (C2.west)
                  edge[vh path] (C3.west)
                  edge[vh path] (C4.west)
      (C1.east)   edge[hv path] (P1.west)
      (C2.east)   edge[hv path] (P2.west)
      (C3.east)   edge[hv path] (P3.west)
      (C4.east)   edge[hv path] (P4.west)
      (endP)      edge[vh path] (P1.east)
                  edge[vh path] (P2.east)
                  edge[vh path] (P3.east)
                  edge[vh path] (P4.east)
                  edge[hv path] (end)
      (startH)    edge[vh path] (H.west)
      (H.east)    edge[hv path] (Hhop1)
      (Hhop1)     edge[thick,out=90,in=90] (Hhop2)
      (Hhop2)     edge[hv path] (P3.south)
                  edge[hv path] (P4.north);
\end{scope}
\end{tikzpicture}
\caption{Reliability block diagram for a simplified automotive brake system
with four component types $M$, $H$, $C$ and $P$.
Note that this system layout cannot be expressed as a nesting of series and parallel layouts.
The corresponding survival signature $\Phi(l_M,l_H,l_C,l_P)$ is given in Table~\ref{tab:brakesys-survsign}.}
\label{fig:brakesys-layout}
\end{figure}

Continuing our example,
the survival signature for the system in Figure~\ref{fig:brakesys-layout} is given in Table~\ref{tab:brakesys-survsign},
omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$.
(The full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.)

\begin{table}
\centering
\begin{tabular}{cccclcccccl}
  \toprule
M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
  \midrule
1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
0 & 1 & 1 & 1 & 0.62 & & 1 & 1 & 1 & 1 & 0.62 \\ 
0 & 1 & 1 & 2 & 0.92 & & 1 & 1 & 1 & 2 & 0.92 \\ 
0 & 1 & 2 & 1 & 0.75 & & 1 & 1 & 2 & 1 & 0.75 \\ 
0 & 1 & 2 & 2 & 0.97 & & 1 & 1 & 2 & 2 & 0.97 \\ 
0 & 1 & 3 & 1 & 0.88 & & 1 & 1 & 3 & 1 & 0.88 \\ 
   \bottomrule
\end{tabular}
\caption{Survival signature $\Phi(l_M, l_H, l_C, l_P)$
for the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout},
omitting the rows for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$.}
\label{tab:brakesys-survsign}
\end{table}

@@

@@

@@

@@
